Exploring dimensions of biodiversity in Japanese ferns

### 2021-05-27 ms/SI.Rmd
Render SI

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
bibliography: "main_library.bib"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
- BoldFont=Roboto-Bold.ttf
- ItalicFont=Roboto-Italic.ttf
- BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
    includes:
      in_header: newphyt.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
# nocite: | 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
```

```{r load-data, cache = FALSE}
# NOTE: This Rmd is meant to be knit as part of the drake plan (R/plan.R).
# If using interactively, run `source("_drake.R")` first.

loadd(list = c(
  "japan_shp",
  "comm_scaled_list_0.1",
  "comm_scaled_list_0.2",
  "comm_scaled_list_0.3",
  "comm_scaled_list_0.4",
  "occ_point_data_ferns",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results"
),
cache = ja_fern_cache)

# Load captions
source(here::here("ms/captions.R"))
```

@@

**`r s_table("phy-sig")`**. `r s_table_cap("phy-sig")` K, Blomberg's *K*; lambda, Pagel's lambda.

@@

**`r s_table("phy-sig-binary")`**. `r s_table_cap("phy-sig-binary")` num_present, number of times a trait was observed present; num_absent, number of times a trait was observed absent; D, Fritz and Purvis' *D*; prob_random, probability of obtaining observed trait distribution given random distribution of traits; prob_brownian, probability of obtaining observed trait distribution given random evolution by Brownian Motion. Presence or absence of indusium was originally a binary trait; other traits (margin, shape, texture) are qualitative traits scored in binary format.

@@

**`r s_figure("sampling-curve")`**. `r s_figure_cap("sampling-curve")` Grey shading indicates 95% confidence interval (not visible where it does not extend beyond the fitted line). Point indicates observed taxonomic richness (`r observed_data$qD` taxa, 95% confidence interval `r rich_interval` taxa). Taxa include species, subspecies, and varieties, excluding hybrids. Sampling completeness is estimated to be `r est_completeness` (95% confidence interval `r completeness_interval`).

@@

# Combine results of building community matrices at different grain sizes
redundancy_by_res <- 
  list(
    "0.1" = comm_scaled_list_0.1$poly_shp,
    "0.2" = comm_scaled_list_0.2$poly_shp,
    "0.3" = comm_scaled_list_0.3$poly_shp,
    "0.4" = comm_scaled_list_0.4$poly_shp) %>%
  map_df(~as_tibble(.) %>% select(grids, abundance, richness), .id = "res") %>%
  # Calculate redundancy
  mutate(redundancy = 1 - (richness/abundance))

@@

**`r s_figure("grain-size")`**. `r s_figure_cap("grain-size")` **A**, Percent of grid cells with redundancy > 0.5 by grain size (0.1, 0.2, 0.3, or 0.4 degree grid-cells). **B**, Percent of grid cells with redundancy = 0 by grain size. **C**, Distribution of redundancy values by grain size. There is a sudden improvement in redundancy values from 0.1 to 0.2 degree grid-cells, but less improvement as grain size is increased beyond 0.2 degrees.

@@

**`r s_figure("abundance")`**. `r s_figure_cap("abundance")`

@@

**`r s_figure("k-plot")`**. `r s_figure_cap("k-plot")` **A**, taxonomic bioregions. **B**, phylogenetic bioregions. Color indicates optimal *k* selected selected by \function{optimal{\_}phyloregion} function in the R package \package{phyloregion} (black, non-optimal; red, optimal; see Methods).

@@

**`r s_figure("raw-biplot")`**. `r s_figure_cap("raw-biplot")` **A**, Phylogenetic diversity (PD). **B**, Relative phylogenetic diversity (RPD). **C**, Functional diversity (FD). **D**, Relative functional diversity (RFD).

@@

**`r s_figure("endemism-restricted")`**. `r s_figure_cap("endemism-restricted")` 'paleo' indicates paleoendemic areas (those with an overabundance of long branches); 'neo' indicates neodendemic areas (those with an overabundance of short branches); 'mixed' indicates significantly endemic sites that have neither an overabundance of short nor long branches; 'super' indicates highly significantly endemic sites that have neither an overabundance of short nor long branches. For details, see Methods.

>>>>

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
bibliography: 
  - references.yaml
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---

```{r setup-si, include = FALSE, cache = FALSE}
# Load functions only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
```

```{r load-data-si, cache = FALSE}
# This Rmd is meant to be knit as part of the target plan (R/_targets.R).
# Run the lines below if rendering outside of targets plan
# library(targets)
# library(tarchetypes)
# source(here::here("R/packages.R"))
# source(here::here("R/functions.R"))

tar_load(c(
  "japan_shp",
  "comm_scaled_list",
  "occ_point_data_ferns",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results"
))
```

```{r load-captions}
# Source captions numbers from MS
# 
# So that caption numbers are in order of appearance in MS

# Run inline code when purling
options(knitr.purl.inline = TRUE)

# Make a temporary file to write out just inline R code from the SI Rmd
temp_file <- tempfile()

# Generate R script including inline R code from the ms Rmd
knitr::purl(here::here("ms/manuscript.Rmd"), output = temp_file)

# Trim this R script down to only functions that define figure and table captions
read_lines(temp_file) %>%
  magrittr::extract(
    str_detect(., "^figure\\(|^table\\(|^s_figure\\(|^s_table\\(|^figure_num\\(|^table_num\\(|^s_figure_num\\(|^s_table_num\\(")
  ) %>%
  unique %>%
  write_lines(temp_file)

# Source the code. This will load the caption functions in the right order.
source(temp_file, local = TRUE)

# Delete the temporary file
fs::file_delete(temp_file)
```

@@

**`r s_table("phy-sig")`**. Phylogenetic signal in continuous functional traits of the ferns of Japan. K, Blomberg's *K*; lambda, Pagel's lambda.

@@

**`r s_table("phy-sig-binary")`**. Phylogenetic signal in quantitative (binary) functional traits of the ferns of Japan. num_present, number of times a trait was observed present; num_absent, number of times a trait was observed absent; D, Fritz and Purvis' *D*; prob_random, probability of obtaining observed trait distribution given random distribution of traits; prob_brownian, probability of obtaining observed trait distribution given random evolution by Brownian Motion. Presence or absence of indusium was originally a binary trait; other traits (margin, shape, texture) are qualitative traits scored in binary format.

@@

**`r s_figure("sampling-curve")`**. Species collection curve for the ferns of Japan fit with the `r pack("iNEXT")` package. Grey shading indicates 95% confidence interval (not visible where it does not extend beyond the fitted line). Point indicates observed taxonomic richness (`r observed_data$qD` taxa, 95% confidence interval `r rich_interval` taxa). Taxa include species, subspecies, and varieties, excluding hybrids. Sampling completeness is estimated to be `r est_completeness` (95% confidence interval `r completeness_interval`).

@@

# Combine results of building community matrices at different grain sizes
redundancy_by_res <- 
  list(
    "0.1" = comm_scaled_list %>% filter(resol == 0.1) %>% pull(poly_shp) %>% pluck(1),
    "0.2" = comm_scaled_list %>% filter(resol == 0.2) %>% pull(poly_shp) %>% pluck(1),
    "0.3" = comm_scaled_list %>% filter(resol == 0.3) %>% pull(poly_shp) %>% pluck(1),
    "0.4" = comm_scaled_list %>% filter(resol == 0.4) %>% pull(poly_shp) %>% pluck(1)
    ) %>%
  map_df(~as_tibble(.) %>% select(grids, abundance, richness), .id = "res") %>%
  # Calculate redundancy
  mutate(redundancy = 1 - (richness/abundance))

@@

**`r s_figure("grain-size")`**. Effect of grain size on sampling redundancy. **A**, Percent of grid cells with redundancy > 0.5 by grain size (0.1, 0.2, 0.3, or 0.4 degree grid-cells). **B**, Percent of grid cells with redundancy = 0 by grain size. **C**, Distribution of redundancy values by grain size. There is a sudden improvement in redundancy values from 0.1 to 0.2 degree grid-cells, but less improvement as grain size is increased beyond 0.2 degrees.

@@

**`r s_figure("abundance")`**. Observed number of specimens (**A**) and sampling redundancy (**B**) per 0.2° grid cell in the ferns of Japan.

@@

**`r s_figure("k-plot")`**. Selection of *k* for bioregions. **A**, taxonomic bioregions. **B**, phylogenetic bioregions. Color indicates optimal *k* selected selected by the `r func("optimal_phyloregion")` function in the R package `r pack("phyloregion")` (black, non-optimal; red, optimal; see Methods).

@@

**`r s_figure("raw-biplot")`**. Relationships between observed functional and phylogenetic diversity and taxonomic richness in the ferns of Japan. **A**, Phylogenetic diversity (PD). **B**, Relative phylogenetic diversity (RPD). **C**, Functional diversity (FD). **D**, Relative functional diversity (RFD).

@@

**`r s_figure("endemism-restricted")`**. Phylogenetic endemism of the ferns of Japan measured using CANAPE (categorical analysis of neo- and paleo-endemism), restricted dataset including only taxa endemic to Japan. 'paleo' indicates paleoendemic areas (those with an overabundance of long branches); 'neo' indicates neodendemic areas (those with an overabundance of short branches); 'mixed' indicates significantly endemic sites that have neither an overabundance of short nor long branches; 'super' indicates highly significantly endemic sites that have neither an overabundance of short nor long branches. For details, see Methods.
